Practical Optional Types for Clojure

### 2015-02-28 overview.tex
experience

\paragraph{HMaps in Practice} The next example is extracted from a production system at CircleCI
(section~\ref{sec:casestudy} presents a case study).

>>>>

\paragraph{HMaps in Practice} The next example is extracted from a production system at CircleCI,
a company with a large production Typed Clojure system
(section~\ref{sec:casestudy} presents a case study).
